Our Galactocentric Coordinate System Is Probably Wrong, and Not by a Little

### 2018-12-11 paper/ms.tex
Update paper

Here we choose to simplify the problem by considering only perfectly circular,
planar orbits. Since these orbits have no phase-dependent structure, we can
work on shorter timescales, i.e. for orbits with significant radial or
vertical action a large fraction of their orbit would need to be sampled in
order to measure the orbit accurately. Because we know the analytic form of
these orbits, we can forward model the trajectory of each star particle in the
cosmological simulation. Working in comoving coordinates, we can write down
the trajectory of a star particle as

\beq
\bm{r}(t) = R(\theta, \phi, \psi) \left( (A\cos{\omega t}, B\sin{\omega t}, C t) + \bm{x_0} \right)
\eeq

@@

We now

>>>>

Here we choose to simplify the problem by considering only perfectly circular,
planar orbits. Since these orbits have no phase-dependent structure, we can
work on shorter timescales, i.e. for orbits with significant radial or
vertical action a large fraction of their orbit would need to be sampled in
order to measure the orbit accurately. Because we know the analytic form of
these orbits, we can forward model the trajectory of each star particle in the
cosmological simulation. Working in comoving coordinates, we can write down
the trajectory of a star particle as
\beq\label{eq:helix}
\bm{r}(t) = R(\theta, \phi, \psi) \left[ (A\cos{\omega t}, B\sin{\omega t}, C
t) + \bm{x_0} \right]\text{,}
\eeq
where $R(\theta, \phi, \psi)$ is an Euler angle transformation, $A$, $B$, $C$,
and $\omega$ are arbitrary constants, and $\bm{x_0}$ is an arbitrary 3-vector.
This equation is a helix with an arbitrary constant and rotation. It describes
the

We minimize the summed squared difference between Equation~\ref{eq:helix} and
the true trajectory of each star with $R$ within $1\,\kpc$ of $R_{\odot} =
8.2\,\kpc$ in each simulation. We consider minimum rms error (i.e. the typical
error in the Equation~\ref{eq:helix} model in describing the true trajectory).
This rms error characterizes how well the helix model we consider, which would
be exactly correct if the overall motion of the galaxy is well-described by
constant speed motion and the orbit of a particular store is exactly circular
and planar.

We plot a histogram of the rms error for each galaxy in
Figure~\ref{fig:something}. As we estimated before, the total effect of the
galaxy's acceleration is roughly $90\,\pc$ (\Gus{Check for m12f, m12m}). We
find that this is small compared to the typical error, even for the stars
whose trajectories are best modeled by Equation~\ref{eq:helix}.

There are many reasons for the failure of this model. First, there could be no
stars on circular orbits. This seems unlikely considering that typical
distribution functions peak on perfectly circular, planar orbits
\citep[e.g.][]{2013MNRAS.434..652T}. Second, the trajectory of the galaxy may
not be well-described by constant-speed motion. This also seems unlikely,
considering that the bulk acceleration of the stellar disk only results in a
$\sim90\,\pc$ (\Gus{m12f, m12m}) deviation from constant-speed motion over the
$22\,\Myr$ time we considered.

Furthermore, in Figure~\ref{fig:something} we plot the center of mass of the
galaxy (in comoving coordinates) for the $22\,\Myr$ timeframe described. The
center of mass at each snapshot is computed using the iterative shrinking
spheres method described in Section~\ref{ssec:cosmozoom}. The rms error on the
constant-speed motion is $\sim\text{something}$, which we interpret as
\Gus{something}.

One potential explanation is that {\em no star can remain on a circular,
planar orbit}. The order unity density variations may be strong enough such
that each star's orbit is perturbed. If there are truly stars in the
simulation on perfectly circular, planar orbits, then the magnitude of their
acceleration over the last $22\,\Myr$ must be constant. Furthermore, their
trajectory in acceleration space must be well-described by a rotation. In the re-runs,

@@

We now repeat the procedure but for
